Incentives are the biggest barriers to widespread data sharing

### 2021-08-04 new-paper.Rmd
Updated to make two sections - one for introduction, one for "Improving the state of resuable data sharing"

## Improving the state of reusable data sharing

@@

# Documentation (READMEs) {#readme}

@@

# Licences {#licenses}

@@

# Metadata {#metadata}

@@

# Raw data vs analysis ready data {#rawdata}

@@

# Data cleaning scripts {#scripts}

@@

# Citation: How you want your data to be cited {#cite}

@@

# Avenues to share data {#avenues}

@@

# Data as part of open source packages {#pkgs}

@@

# Considerations for data size {#size}

>>>>

# Improving the state of reusable data sharing

@@

## Documentation (READMEs) {#readme}

@@

## Licences {#licenses}

@@

## Metadata {#metadata}

@@

## Raw data vs analysis ready data {#rawdata}

@@

## Data cleaning scripts {#scripts}

@@

## Citation: How you want your data to be cited {#cite}

@@

## Avenues to share data {#avenues}

@@

## Data as part of open source packages {#pkgs}

@@

## Considerations for data size {#size}
